A graph-based data model for interactive evolutionary computation

### 2017-01-18 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Working just on the Intro

\section{Introduction}
% Maybe an introduction on why and where to use these types of
% algorithms? - jj
% Done -Mario
Interactive Evolutionary Algorithms (IEAs) are standard EAs whose
fitness evaluations are performed by persons within an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution.
IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IECs have been developed as web based systems \cite{picbreeder},
who depend on volunteers who visit the system to interactively help
with the search, using both anonymous and registered users.
These systems have several inherent drawbacks arising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction,
boredom or lack of interest when evaluating a large number of individuals,
many of which are not interesting or are very similar to each other.
IEAs share some of the issues commonly found in volunteer based systems
\cite{sarmenta2001volunteer,web:BOINC} such as volunteer\'s lack of accountability,
the need to build trust between participants and application providers. 
There is also the difficulty of establishing the amount of time and resources
a volunteer is willing to spend on the system, and how they decide if they
participate or not \cite{JJ:2016}.

 % Can it be quantified? Maybe a reference to NodIO? - JJ
Some authors have already tried to address this basic problem
\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj

% Maybe this claim should go to the beginning. THIS is why we want to
% use them - JJ
 In particular
the EvoSpace-Interactive (ES-I) %citation
platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, individuals about individuals %what? Maybe data
                                %about individuals? - JJ
must be stored, even
if they are no longer in the active population. In this work a graph database
is proposed to model the interaction between users and individuals, with
the following advantages:

>>>>

\section{Introduction}
% Maybe an introduction on why and where to use these types of
% algorithms? - jj
% Done -Mario
Interactive Evolutionary Algorithms (IEAs) are standard EAs whose
fitness evaluations are performed by persons within an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution.
IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IECs have been developed as web based systems \cite{picbreeder},
who depend on volunteers who visit the system to interactively help
with the search, using both anonymous and registered users.
These systems have several inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of individuals 
many of which are not interesting or are very similar to each other.
IEAs also share some of the issues commonly found in volunteer based systems
\cite{sarmenta2001volunteer,web:BOINC} such as the volunteer\'s lack of accountability,
and the need to build trust between participants and application providers. 
There is also the difficulty of establishing the amount of time and resources
a volunteer is willing to spend on the system, and how they decide if they
participate or not \cite{JJ:2016}. In order to increase participation and 
engagement, and to tackle the issues mentioned above,  
IEAs must follow a user centered design, giving extensive attention 
to volunteer users, not only because their
explicit evaluation is essential, but also because the context of the 
interaction affects the system as a whole. Users interact not only with the graphical
interface, and each individual\'s phenotype, there is also the interaction
with other users, their previous evaluations and their own stream of activities
and past experiences. Thus users in this proposal are defined as dynamic entities 
interacting with an evolutionary computation having the fundamental purpose 
of evaluating individuals according to their preferences,
both explicitly or implicitly. In this work we propose giving the same
importance to users and their interactions as the population of 
individuals have in a traditional EA, even to the extend as using this
knowledge as an integral part of the algorithm it self. We argue also
that a graph model is a viable representation for this purpose.

% Moving to related work - Mario
%\cite{Performance for the masses and Christian's previous work},

 % Can it be quantified? Maybe a reference to NodIO? - JJ
%Some authors have already tried to address this basic problem
%\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj
%% Moving this to Related Work Section -Mario

% Maybe this claim should go to the beginning. THIS is why we want to
% use them - JJ
% Done - Mario

As a proof of concept, a case study is presented providing both 
conceptual and implementation details using the EvoSpace-Interactive
platform.

the EvoSpace-Interactive (ES-I) %citation
platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, individuals about individuals %what? Maybe data
                                %about individuals? - JJ
must be stored, even
if they are no longer in the active population. In this work a graph database
is proposed to model the interaction between users and individuals, with
the following advantages:
